\beginsong{Off to Sea}[
    by={The Longest Johns}
]

\begin{infotext}
Im Original wird es in Standardstimmung mit Capo auf dem 3.~Bund gespielt.\\
Für mich funktioniert es besser mit Capo auf dem 1.~Bund.
\end{infotext}

\newchords{off_to_sea_verse}
\newchords{off_to_sea_chorus}

\textnote{Fingerstyle}

\beginverse\memorize[off_to_sea_verse]
When \[Am]first I landed in \[G]Liverpool I \[F]went u\[G]pon the \[Am]spree.
With \[Am]money at last, I \[C/G]spent it fast, I got \[Am]drunk as drunk could \[G]be.
But \[C/G]when my money \[G]was all gone it was \[Am]then that I wanted \[G]more. \[G/G#]
But a \[Am]man must be blind to \[G]make up his mind to \[F]got to \[G]sea once \[Am]more.
\endverse

\textnote{Strumming}

\beginchorus\memorize[off_to_sea_chorus]
Once \[C/G]more, once \[G]more, \[Am]go to sea once \[G]more. \[G/G#]
But a \[Am]man must be blind to \[G]make up his mind to \[F]go to \[G]sea once \[Am]more.
\endchorus

\beginverse\replay[off_to_sea_verse]
And ^as I walked down ^London road I ^met with a ^Rapper ^Brown
I ^asked him if he'd ^take me in and he ^looked at me with a ^frown
He ^said, \enquote{Last time you ^was paid off, to ^me you chaulked no ^score} ^
\enquote{But I'll ^give you a chance and I'll ^take your advance
And I'll ^send you to ^sea once ^more.}
\endverse

\beginchorus\replay[off_to_sea_chorus]
Once ^more, once ^more, ^send you to sea once ^more ^
But I'll ^give you a chance and I'll ^take your advance
And I'll ^send you to ^sea once ^more
\endchorus

\beginverse\replay[off_to_sea_verse]
I ^shipped onboard of a ^whaling barque, we were ^bound for the ^Greenland ^seas
Where ^cold winds blow through ^frost and snow why Ja^maica rum would ^freeze
And ^worst to bear, I'd no ^hard weather gear as I'd ^spent all my money ^ashore ^
It was ^then that I wished that ^I was dead and could ^go to ^sea no ^more
\endverse

\beginchorus\replay[off_to_sea_chorus]
No ^more, no ^more, ^go to sea no ^more ^
It was ^then that I wished that ^I was dead and could ^go to ^sea no ^more
\endchorus

\beginverse\replay[off_to_sea_verse]
Some^times we're catching ^whales, me lads, some^times we're ^catching ^none
With a ^20-foot oar stuck ^in your paw from ^four o'clock in the ^morn
And ^as the shades of ^night roll on and you ^rest on your weary ^oar ^
It was ^then that I wished that ^I was dead and could ^go to ^sea no ^more
\endverse

\beginchorus\replay[off_to_sea_chorus]
No ^more, no ^more, ^go to sea no ^more ^
It was ^then that I wished that ^I was dead and could ^go to ^sea no ^more
\endchorus

\textnote{Fingerstyle}

\beginverse\replay[off_to_sea_verse]
So come ^all of you hard weather-^sailing lads who ^listen ^to my ^song
When ^you get back from ^those long trips I'd ^have you not go ^wrong
Take ^my advice, drink ^no strong drink, don't you ^knock on that brothel ^door ^
But get ^married instead and spend ^all night in bed and ^go to ^sea no ^more
\endverse

\textnote{Strumming}

\beginchorus\replay[off_to_sea_chorus]
No ^more, no ^more, ^go to sea no ^more ^
But get ^married instead and spend ^all night in bed and ^go to ^sea no ^more.
\endchorus

\beginchorus\replay[off_to_sea_chorus]
No ^more, no ^more, ^go to sea no ^more ^
But get ^married instead and spend ^all night in bed and ^go to ^sea no \[Am add9]more.
\endchorus


\endsong

