\beginsong{Snuff}[
	by={Slipknot}
]

\newchords{snuff_verse}
\newchords{snuff_chorus}

\beginverse*
\[Am] \[Em] \[Fmaj7] \[C]
\endverse

\beginverse\memorize[snuff_verse]
\[Am]Bury all your secrets \[Em]in my \[Fmaj7]skin \[C]---
\[Am]Come away with innocence, \[Em]and \[Fmaj7]leave me with my sins \[C]---
The \[Am]air around me still feels \[Em]like a \[Fmaj7]cage \[C]---
And \[Am]love is just a camouflage \[Em]for \[Fmaj7]what resembles rage a\[C]gain.
\endverse

\beginverse*
\[Am] \[Em] \[Fmaj7] \[C]
\[Am] \[Em] \[Fmaj7]
\endverse

\beginchorus\memorize[snuff_chorus]
So if you love me, let me \[G]go. And run away before \[Am]I know.
My heart is just too dark \[G]to care. I can't destroy what isn't \[Am]there.
Deliver me into my \[G]Fate. If I'm alone I cannot \[Am]hate
I don't deserve to have \[G]you,
My \[Fmaj7]smile was taken long ago, if I can change I hope I never \[Am]know
\endchorus

\beginverse*
\[Am] \[Em] \[Fmaj7] \[C]
\[Am] \[Em] \[Fmaj7] \[C]
\endverse

\beginverse\replay[snuff_verse]
I ^still press your letters ^to my ^lips ^---
And ^cherish them in parts of me ^that ^savor every kiss ^---
I ^couldn't face a life without ^your ^light ^---
But ^all of that was ripped apart, ^when \[F]you refused to fight
\endverse

\beginchorus\replay[snuff_chorus]
So save your breath, I will not ^care. I think I made it very ^clear.
You couldn't hate enough ^to love. Is that supposed to be e^nough.
I only wish you weren't ^my friend, Then I could hurt you in ^the end.
I never claimed to be a ^Saint,
Ooh, my ^own was banished long ago. It took the Death of Hope to let you ^go.
\endchorus

\beginverse*
\lrep \[Am] \[Em] \[Fmaj7] \[C] \rrep \rep{3}
\[Am] \[Em] \[Fmaj7]
\endverse

\beginchorus\replay[snuff_chorus]
So break yourself against my ^stones and spit your pity in ^my soul.
You never needed any ^help, you sold me out to save ^yourself.
And I won't listen to ^your shame. You ran away, you're all the ^same.
Angels lie to ^keep control.
My \[F]love was punished long ago
If you still care, don't ever let me \[Am]know. \[Em] \[F]---
If you still care, don't \[C]ever let me \[Am]kno---ow.
\[Em] \[Fmaj7] \[C] \[Am]
\endchorus

\endsong