\beginsong{Star of the County Down}[
	by={Traditional}
]

\beginverse
Near \[Em]Banbridge \[C]town, in the \[G]County \[D]Down,
One \[Em]morning in \[D]July,
Down a \[Em]boreen \[C]green came a \[G]sweet \[D]colleen
And she \[Em]smiled as she passed me \[C]by;
She \[D]looked so \[Em]sweet \[G]from her \[D]two bare feet,
To the \[Em]sheen of her nut-brown \[D]hair,
Such a \[Em]coaxing \[C]elf, I shure \[G]shook my\[D]self,
To make \[Em]sure I was \[C]real\[D]ly \[Em]there.
\endverse

\beginverse
As she ^onward ^sped sure I ^scratched my ^head
And I ^said with a feeling ^quare
And I ^said, says ^I to a ^passer-^by.
Who's the ^maid with the nut-brown ^hair?
Oh, he ^smiled at ^me, ^and with ^pride says he
That's the ^gem of Ireland's ^crown.
She's young ^Rosie Mc^Cann, from the ^banks of the ^Bann
She's the ^star of the ^Coun^ty ^Down.
\endverse

\beginchorus
Oh, from \[G]Bantry Bay up to \[D]Derry Quay,
And from \[Em]Galway to Dublin \[D]town
No \[Em]maid I've \[C]seen like the \[G]fair col\[D]leen,
That I \[Em]met in the \[C]Coun\[D]ty \[Em]Down.
\endchorus

\beginverse
She'd a ^soft brown ^eye and a ^look so ^sly,
And a ^smile like the rose in ^June,
And you ^hung on each ^note from her ^lily-white ^throat,
As she ^lilted an Irish ^tune.
At the ^pattern ^dance ^you were ^held in trance
As she ^tripped through a reel or ^jig,
And when her ^eyes she'd ^roll, she'd ^coax upon my ^soul
A ^spud from a ^hung^ry ^pig.
\endverse

\beginverse
I've ^travelled a ^bit, but ^never was ^hit,
Since my ^roving career be^gan;
But ^fair and ^square I sur^rendered ^there
To the ^charm of young Rose Mc^Cann.
With a ^heart to ^let ^and no ^tenant yet
Did I ^meet within shawl or ^gown
But ^in she ^went and I ^asked no ^rent
From the ^star of the ^Coun^ty ^Down.
\endverse

\beginverse
At the ^harvest ^fair I'll be ^surely ^there
And I'll ^dress in my Sunday ^clothes,
With my ^shoes shone ^bright and my ^hat up^right
And a ^smile from my nut-brown ^Rose.
No ^pipe I'll ^smoke, ^no ^horse I'll yoke
Though my ^plough with rust turns ^brown
Till a ^smiling ^bride by my ^own fire^side
Sits the ^Star of the ^Coun^ty ^Down.
\endverse
\endsong