\beginsong{The Bard's Song}

\beginverse*
\[Am]Now You all \[G]know,
The \[Em7]bards and their \[Am]songs.
\endverse

\beginverse\memorize
\[Am]When hours have gone \[G]by,
\[Em7]I'll close my \[Am]eyes.
In a \[Am]world far a\[G]way,
We \[Em7]may meet a\[Am]gain.
But \[Am]now hear my \[G]song,
About the \[Em7]dawn of the \[Dm]night.
Let's \[C]sing \[G]the \[Am]bards' \[G]song..
\endverse

\beginchorus
To\[Dm]mor\[Am]row will \[Dm]take us \[Am]away,
\[Dm]Far from \[Am]home,
\[Dm]No one will \[F]ever \[G]know our \[Dm]names,
But the \[Am]bards' songs \[G]will re\[Am]main.
To\[Dm]mor\[Am]row will \[Dm]take it \[Am]away,
The \[Dm]fear of \[Am]today,
\[Dm]It will be \[Fm]gone,
Due \[Em]to \[C]our magic \[Am]songs.
\endchorus

\beginverse
There's ^only one ^song,
^Left in my ^mind.
^Tales of a ^brave man,
Who ^lived far from ^here.
Now the ^bard songs are ^over,
And ^it's time to ^leave.
\[Am]No one should \[G]ask You for the \[Em7]name Of the \[Dm]one,.
Who \[C]tells \[G]the \[Am]sto\[G]ry.
\endverse

\beginchorus
To\[Dm]mor\[Am]row will \[Dm]take us \[Am]away,
\[Dm]Far from \[Am]home,
\[Dm]No one will \[F]ever \[G]know our \[Dm]names,
But the \[Am]bards' songs \[G]will re\[Am]main.
To\[Dm]mor\[Am]row \[Dm]all will be \[Am]known,
And \[Dm]You're not a\[Am]lone,
So \[Dm]don't be a\[F]fraid,
In the \[G]dark and \[Dm]cold,
\[Am]'Cause the bards' songs will \[F]rema\[C]in \[Dm],
They \[F]all \[C]will re\[Dm]main.
\endchorus

\beginverse
\[C]In my \[G]thoughts and \[Am]in my dreams,
They're \[C]always \[G]in my \[Am]mind,
These \[C]songs of \[G]hobbits, \[Am]dwarves and men,
And \[C]elves, Come \[G]close Your \[Am]eyes..
You can \[C]see \[G]them, \[Em]too..
\endverse
\endsong