\beginsong{Tribute}[
	by={Tenacious D}
]

\beginverse*
\[Am]This is the greatest and best song in the world...
\[Am]Tribute.
\endverse

\beginverse
\[Am]Long time ago me and my brother Kyle here,
\[Am]We was hitchhikin' down a long and lonesome road.
\[Am]All of a sudden, there shined a shiny demon...
\[Am]In the middle of the road.
\[Am]And he said:

\vspace*{1em}

\textnote{Gedämpfte Achtel auf A-Saite}
Play the best song in the world, or I'll eat your souls.

\vspace*{1em}
\[Am]Well me and Kyle, we looked at each other,
\[Am]And we each said...   "Okay"
\endverse

\beginverse*
And we \[Am]played the first thing that \[G]came to our heads,
\[F]Just so happened to be,
The \[Am]Best Song in the \[G]World, it was The \[F]Best Song in the World.
\endverse

\beginchorus
\[D]Look into my eyes and it's \[F]easy to see
One and \[C]one make two, two and \[G]one make three,
It was \[F]destiny.

\vspace*{1em}

\[D]Once every hundred-thousand \[F]years or so,
When the \[C]sun doth shine and the \[G]moon doth glow
And the \[F]grass don't grow...
\endchorus

\beginverse
\[Am]Needless to say, the beast was stunned.
\[Am]Whip-crack went his schwumpy tail,
\[Am]And the beast was done.
\[Am]He asked us: "Be you angels?"
\[Am]And we said, "Nay. We are but men!" ROCK!
\endverse

\beginverse*
\[D]Ahhh,\[F] ahhh, \[C]ahhh-ah-\[G]ah,
\[F]Ohhh, whoah, ah-whoah-oh!
\endverse

\beginchorus
\[Am]--- This is not The \[G]Greatest Song in the \[Am]World.
\[Am]No, this is just a \[G]tribute. \[Am]---
\[Am]--- Couldn't remember The \[G]Greatest Song in the\[Am] World.
\[Am]No, this is a \[G]tribute, \[Am]oh.

\vspace*{1em}

\[Am]--- \[G]To The Greatest \[D]Song in the \[F]World, All right!
\[Am]--- \[G]It was The Greatest \[D]Song in the \[F]World, All right!
\[Am]It was the \[G]best muthafuckin' song
The \[D]greatest song in the \[F]world.
\endchorus

\textnote{Ohne Begleitung}
\beginverse*
Dee soo guh goo gee goo gee
Goo guh fli-goo gee goo, guh fli-goo ga goo buh dee
Ooh guh goo bee, ooh guh guh bee guh guh bee
Fli-goo gee goo, a-fli-guh woo wa mama Lucifer!
\endverse

\beginverse*
\[Am] \[G] \[D] \[F]
\[Am] \[G] \[D] \[F]
\endverse

\beginverse*
\[Am]And the peculiar \[G]thing is this my friends:
\[D]The song we sang on that \[F]fateful night,
It \[Am]didn't actually \[G]sound anything like this \[D]song. \[F]
\endverse

\beginverse
This is just a \[Am]tribute! You \[G]gotta' be\[D]lieve me! \[F]
And I wish you were \[Am]there! Just a \[G]matter of o\[D]pinion. \[F]
Ah,what the fuck! \[Am]Good God, \[G]Gotta love 'em,
\[D]--- So surprised to \[F]find you can't stop me now.
The \[Am]fiery \[G]ring of fire!
\[D]Ritsss motherfucker, \[F]the perfect song!
\endverse

\beginverse*
\[E] \[F] All \[E]right! \[F] 
\[E] \[F] All \[E]right! \[F]
\[E] \[F] \[F] \[F]
\endverse

\endsong